---
title: "Chinook Troll + Sport AY 2018"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

# Introduction

## Goals & Objectives

The goal of this R Notebook is to analyze Chinook salmon mixtures from SEAK troll, sport, and THA fisheries for AY 2018. The individuals mixtures are indicated below by fishery:

  * Troll
    + Early Winter
        - NO
        - SONISI
    + Late Winter
        - NO
        - SONISI
    + Spring 1 (May)
        - 10145 - 200 fish
        - 10350 - 200 fish
        - 11341 - 200 fish
    + Spring 2 (June)
        - 10145 - 200 fish
        - 10350 - 200 fish
        - 11301 - 200 fish
        - 11341 - 200 fish
        - 11362 - 200 fish
    + Spring overall
        - 11330 - 100 fish
        - 18310 - 100 fish
    + Summer 1
        - NO
        - SO
        - NI
        - SI
    + Summer 2
        - NO
        - SO
        - NI
        - SI
  * Sport
    + Outside
        - Through BW 13
        - After BW 13
    + Petersburg-Wrangell (PBG-WRN)
    + Juneau (JNU)
    + Ketchikan (KTN)
    + Sitka (SIT)
    + Craig (CRG)
  * THA
    + 10195 (Neets Bay)
        - SW 18-23
        - SW 24
        - SW 25-27
    + 10735 (Anita Bay)
        - SW 20-21
        - SW 22
        - SW 23
        - SW 24
        - SW 25-30

We are going to run everything for 33 reporting groups and then summarise from there for whoever needs it.

## Outline

This R Notebook will:

1) Import mixture genotypes
2) Join ASL
3) Define mixture strata
3) Data QA
4) Create *BAYES* files
5) Summarize *BAYES* results
6) Output tables

## Setup

Load *GCL-R-Functions* and all necessary packages.
```{r setup, message=FALSE, results='hide'}
source("~/../R/Functions.GCL.R")
library(tidyverse)
library(lubridate)

.username <- "krshedd"
.password <- ""
```

Read in those objects and `LocusControl`
```{r load_objects}
load_objects("../Objects/")
```


# Winter troll: import mixture genotypes

Read in genotypes from *LOKI* as `.gcl` objects. Save in directory.
```{r winter_loki}
# origins_sillys <- c("KTROL17EW", "KTROL18LW", "KTROL18SP", "KTROL18SU", "KSPORT18", "KTROL18THA", "KGILL18THA", "KSEIN18THA", "KSEIN18CR")
winter_2018_sillys <- c("KTROL17EW", "KTROL18LW")
LOKI2R_GAPS.GCL(sillyvec = winter_2018_sillys, username = .username, password = .password)
rm(.username, .password)

sapply(winter_2018_sillys, function(silly) {get(paste0(silly, ".gcl"))$n} )

save_sillys(sillyvec = winter_2018_sillys, path = "../Genotypes/original")
save_objects(objects = c("winter_2018_sillys"), path = "../Objects/")
```

# Join ASL

## Winter Troll

Read in the troll ASL data.
```{r troll_asl, message=FALSE}
(troll_ASL <- read_csv(file = "../ASL Data/20190204_troll_2017_2018_Detailed ASL Samples.csv") %>% 
   select(`Sample Date`, `Stat Week`, `Port Code`, `Gear`, `District`, `Dna Specimen No`, `Cwt Strap Tag No`, `Gear Code`, `Harvest Code`))

# Any duplicate Dna Specimen No?
table(table(troll_ASL$`Dna Specimen No`, useNA = "always"), useNA = "always")
```

Shit, it looks like we have some duplicate Dna Specimen No (34 to be precise).
```{r asl_duplicates}
asl_duplicates <- troll_ASL %>% 
  group_by(`Dna Specimen No`) %>% 
  summarise(n = n()) %>% 
  filter(n > 1) %>% 
  pull(`Dna Specimen No`)

troll_ASL %>% 
  filter(`Dna Specimen No` %in% asl_duplicates) %>% 
  arrange(`Dna Specimen No`)
```

Are any of these fish in our winter troll samples?
```{r asl_duplicates_winter_troll}
early_winter_samples <- KTROL17EW.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  pull(`Dna Specimen No`)

any(early_winter_samples %in% asl_duplicates)

late_winter_samples <- KTROL18LW.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  pull(`Dna Specimen No`)

any(late_winter_samples %in% asl_duplicates)
```

Cool, none of our ASL duplicate Dna Specimen No are in there. Now verify that all winter samples are in the ASL data.
```{r winter_in_asl}
all(early_winter_samples %in% troll_ASL$`Dna Specimen No`)
all(late_winter_samples %in% troll_ASL$`Dna Specimen No`)
```

Which early winter sample(s) are missing?
```{r early_winter_missing}
# Which sample is missing from ASL?
(early_missing <- setdiff(early_winter_samples, troll_ASL$`Dna Specimen No`))

# Does that WGC exist?
troll_ASL %>% 
  mutate(WGC_4char = str_sub(`Dna Specimen No`, 1, 4)) %>% 
  filter(WGC_4char == str_sub(early_missing, 1, 4))

# Did we extract this fish?
EW_torun_ASL.df %>% 
  filter(`Dna Specimen No` == early_missing)

# Nope, we did not extract this fish
setdiff(early_winter_samples, EW_torun_ASL.df$`Dna Specimen No`)

# What fish did we attempt to extract, but not get?
setdiff(EW_torun_ASL.df$`Dna Specimen No`, early_winter_samples)
```

WTF, what is the deal with this fish? Probably mixed up with 549901
```{r early_winter_missing_cont}
KTROL17EW.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  filter(`Dna Specimen No` %in% early_missing)

troll_ASL %>% 
  filter(`Dna Specimen No` == 549901)
```

I went out to the warehouse to pull the WGC and confirmed that the ASL data is incorrect, the card Dna Specimen No should be 459901, not 549901

```{r early_winter_missing_fix}
troll_ASL <- troll_ASL %>% 
  mutate(`Dna Specimen No` = case_when(`Dna Specimen No` == 549901 ~ 459901,
                                       TRUE ~ `Dna Specimen No`))
```

Now that we've resolved our ASL discrepancy, join with attributes to get quadrant level information.
```{r join_winter_asl}
# Join ASL with attributes table
# Early Winter
KTROL17EW.gcl$attributes <- KTROL17EW.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(troll_ASL, by = "Dna Specimen No")

# Late Winter
KTROL18LW.gcl$attributes <- KTROL18LW.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(troll_ASL, by = "Dna Specimen No")
```

How many fish per district?
```{r winter_district_counts}
KTROL17EW.gcl$attributes %>% 
  count(District)

KTROL18LW.gcl$attributes %>% 
  count(District)
```

# Define mixture strata

Winter mixtures are each quadrant by itself.

Create early winter mixtures.
```{r early_winter_define_mixtures}
EWintNO_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 171)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintNO_2018.vials, newname = "EWintNO_2018")

EWintSO_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 172)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintSO_2018.vials, newname = "EWintSO_2018")

EWintNI_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 173)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintNI_2018.vials, newname = "EWintNI_2018")

EWintSI_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 174)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintSI_2018.vials, newname = "EWintSI_2018")

sapply(grep(pattern = "EWint", objects(pattern = "\\.gcl"), value = TRUE), function(silly) {get(silly)$n})
```

Create late winter mixtures.
```{r late_winter_define_mixtures}
LWintNO_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL18LW", attribute = "District", matching = 171)), nm = "KTROL18LW")
PoolCollections.GCL(collections = "KTROL18LW", loci = GAPSLoci_reordered, IDs = LWintNO_2018.vials, newname = "LWintNO_2018")

LWintSO_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL18LW", attribute = "District", matching = 172)), nm = "KTROL18LW")
PoolCollections.GCL(collections = "KTROL18LW", loci = GAPSLoci_reordered, IDs = LWintSO_2018.vials, newname = "LWintSO_2018")

LWintNI_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL18LW", attribute = "District", matching = 173)), nm = "KTROL18LW")
PoolCollections.GCL(collections = "KTROL18LW", loci = GAPSLoci_reordered, IDs = LWintNI_2018.vials, newname = "LWintNI_2018")

LWintSI_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL18LW", attribute = "District", matching = 174)), nm = "KTROL18LW")
PoolCollections.GCL(collections = "KTROL18LW", loci = GAPSLoci_reordered, IDs = LWintSI_2018.vials, newname = "LWintSI_2018")

sapply(grep(pattern = "LWint", objects(pattern = "\\.gcl"), value = TRUE), function(silly) {get(silly)$n})
```

Save genotypes for winter strata.
```{r save_winter_strata_genotypes}
if(!dir.exists("../Genotypes/strata")) {dir.create("../Genotypes/strata")}

winter_2018_mixnames <- c(paste0("EWint", c("NO", "SO", "NI", "SI"), "_2018"), 
                          paste0("LWint", c("NO", "SO", "NI", "SI"), "_2018"))

save_objects(objects = "winter_2018_mixnames", path = "../Objects/")
save_sillys(sillyvec = winter_2018_mixnames, path = "../Genotypes/strata/")
```

# Data QA

Standard data QA:

  * Remove fish missing <80% genotypes
  * Remove duplicates (>95% genotype concordance)

```{r QA}
# original sample sizes
winter_2018_sample_sizes <- tibble(silly = winter_2018_mixnames,
                                   genotyped = sapply(winter_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# missing
winter_2018_missing <- RemoveIndMissLoci.GCL(sillyvec = winter_2018_mixnames, proportion = 0.8)
save_objects("winter_2018_missing", "../Objects/")

winter_2018_sample_sizes <- winter_2018_sample_sizes %>% 
  mutate(missing = genotyped - sapply(winter_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# duplicate
winter_2018_duplicates <- CheckDupWithinSilly.GCL(sillyvec = winter_2018_mixnames, loci = GAPSLoci_reordered, quantile = NULL, minproportion = 0.95)
(winter_2018_duplicates_summary <- sapply(winter_2018_mixnames, function(x) {winter_2018_duplicates[[x]]$report}))
save_objects("winter_2018_duplicates_summary", "../Objects/")

winter_2018_duplciates_removed <- RemoveDups.GCL(dupcheck = winter_2018_duplicates)

winter_2018_sample_sizes <- winter_2018_sample_sizes %>% 
  mutate(duplicate = genotyped - missing - sapply(winter_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# final
winter_2018_sample_sizes <- winter_2018_sample_sizes %>% 
  mutate(final = sapply(winter_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))
winter_2018_sample_sizes
save_objects("winter_2018_sample_sizes", "../Objects/")

write_csv(winter_2018_sample_sizes, "../Tables/winter_2018_sample_sizes.csv")
```

Save post-QA genotypes
```{r post_QA}
if(!dir.exists("../Genotypes/strata_postQA/")) {dir.create("../Genotypes/strata_postQA/")}
save_sillys(sillyvec = winter_2018_mixnames, path = "../Genotypes/strata_postQA")
```

# Create *BAYES* files

## Directory setup

First need to set up *BAYES* directory structure and copy over baseline file and *BAYES* objects. This was already done when we ran TBR.
```{r BAYES_setup, results='hide'}
# dir.create(path = "../BAYES")
# sapply(c("Baseline", "Control", "Mixture", "Output"), function(folder) {dir.create(path = paste("../BAYES", folder, sep = "/"))} )
# 
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/SEAKPops357.txt", to = "../Objects")
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/bayesfortran_357.txt", to = "../Objects")
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/BAYES/Baseline/GAPS357pops13loci.bse", to = "../BAYES/Baseline")
# file.copy(from = "V:/Analysis/4_Westward/Sockeye/KMA Commercial Harvest 2014-2016/Mixtures/Objects/WASSIPSockeyeSeeds.txt", to = "../Objects")
# 
# TBR_mixnames <- setNames(c("D108Gill_2018", "D111Gill_2018", "D111Sport_2018"), TBR_sillys)
# save_objects("TBR_mixnames", "../Objects/")
# load_objects("../Objects/")
```

## Create mixtures

Save the fortran format and create TBR *BAYES* mixture files. This was already done when we ran TBR.
```{r BAYES_mixtures}
# mixfortran <- CreateMixture.GCL(sillys = TBR_sillys[1], loci = GAPSLoci_reordered, IDs = NULL, mixname = TBR_mixnames[TBR_sillys[1]], dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
# save_objects("mixfortran", "../Objects/")

sapply(winter_2018_mixnames, function(mix) {
  CreateMixture.GCL(sillys = mix, loci = GAPSLoci_reordered, IDs = NULL, mixname = mix, dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
} )
```

## Create priors

New this year, I will be analyzing **ALL** Chinook mixtures with the full 33 reporting groups. However, since I ran last year's troll mixtures for just the 26 reporting groups, I will have to mess with the priors a bit. Also a new wrinkle because we've previously ran NISISO together for Early and Late Winter. I think to keep things simple, I'll use the previous year's NISISO estimate for the prior for each of those respective quadrants (NI, SI, and SO)
```{r read_2017_estimates}
EWint_2017_26RG_EstimatesStats <- dget("../../SEAK17/Estimates objects/EWint_2017_26RG_EstimatesStats.txt")
LWint_2017_26RG_EstimatesStats <- dget("../../SEAK17/Estimates objects/LWint_2017_26RG_EstimatesStats.txt")

(winter_2017_means <- sapply(c(EWint_2017_26RG_EstimatesStats, LWint_2017_26RG_EstimatesStats), function(mix) {mix[, "mean"]}))
```

My plan is to keep the same prior for the 26 groups and then spread out the prior evenly across all other 33 reporting groups.
```{r setup_2018_priors}
# Convert from 26RG to 33RG
winter_2017_means_33RG <- apply(winter_2017_means, 2, function(mix) {mix[GroupVec33RG_to26RG] / table(GroupVec33RG_to26RG)[GroupVec33RG_to26RG]} )
rownames(winter_2017_means_33RG) <- GroupNames33

# Duplicate NISISO to NI, SI, SO
winter_2017_means_33RG <- winter_2017_means_33RG[, c(1, 2, 2, 2, 3, 4, 4, 4)]

# Fix dimnames
colnames(winter_2017_means_33RG) <- winter_2018_mixnames

# Verify
apply(winter_2017_means_33RG, 2, sum)
```

Now create 2018 priors.
```{r create_2018_priors}
winter_2018_priors <- apply(winter_2017_means_33RG, 2, function(mix) {
  Prior.GCL(groupvec = GroupVec33RG_357, groupweights = mix, minval = 0.01)
} )
colnames(winter_2018_priors) <- winter_2018_mixnames
save_objects("winter_2018_priors", "../Objects/")
```

## Create control files

Now that we have priors, just need to create *BAYES* control files.
```{r BAYES_control}
sapply(winter_2018_mixnames, function(mix) {
  CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = mix, basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                        nchains = 5, groupvec = GroupVec33RG_357, priorvec = winter_2018_priors[, mix], initmat = GAPS357PopsInits, 
                        dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                        basefortran = bayesfortran_357, switches = "F T F T T T F")
} )

```

## Create output directories

```{r BAYES_output}
sapply(winter_2018_mixnames, function(mix) {dir.create(paste0("../BAYES/Output/", mix))} )
```

# Summarize *BAYES* results

Summarize results for both the full 33 reporting groups, the 5 TBR groups, 3 TBR groups, and 2 TBR groups.

## 33 reporting groups

Create standard summary and save.
```{r winter_BAYES_summarise_33RG}
# full 33 reporting groups
EWint_2018_33RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, maindir = "../BAYES/Output", mixvec = winter_2018_mixnames[1:4],
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

LWint_2018_33RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, maindir = "../BAYES/Output", mixvec = winter_2018_mixnames[5:8],
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# dir.create("../Estimates objects")
save_objects(c("EWint_2018_33RG_EstimatesStats", "LWint_2018_33RG_EstimatesStats"), "../Estimates objects")
```

Make in to tall tibble.
```{r winter_BAYES_33RG_tibble}
# make in to a tidy tibble (tall)
winter_2018_33RG_estimates.tdy <- 
  bind_rows(
    lapply(winter_2018_mixnames, function(mix) {  # loop over mixture names
      c(EWint_2018_33RG_EstimatesStats, LWint_2018_33RG_EstimatesStats)[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("fishery", "quadrant"), sep = 5) %>%  # extract district and gear
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames33))  # factor for ordering

save_objects(c("winter_2018_33RG_estimates.tdy"), "../Estimates objects")
```


# THA: import mixture genotypes

Read in genotypes from *LOKI* as `.gcl` objects. Save in directory.
```{r THA_loki}
# origins_sillys <- c("KTROL17EW", "KTROL18LW", "KTROL18SP", "KTROL18SU", "KSPORT18", "KTROL18THA", "KGILL18THA", "KSEIN18THA")
THA_2018_sillys <- c("KTROL18THA", "KGILL18THA", "KSEIN18THA")
LOKI2R_GAPS.GCL(sillyvec = THA_2018_sillys, username = .username, password = .password)
rm(.username, .password)

sapply(THA_2018_sillys, function(silly) {get(paste0(silly, ".gcl"))$n} )

save_sillys(sillyvec = THA_2018_sillys, path = "../Genotypes/original")
save_objects(objects = c("THA_2018_sillys"), path = "../Objects/")
```

# Join ASL

## THA

Read in the THA ASL data.
```{r THA_asl, message=FALSE}
(THA_ASL <- read_csv(file = "../ASL Data/20181213_terminal_Harvest - Detailed ASL Samples.csv") %>% 
   select(`Sample Date`, `Stat Week`, `Port Code`, `Gear`, `Stat Area`, `Dna Specimen No`, `Cwt Strap Tag No`, `Gear Code`, `Harvest Code`))

# Any duplicate Dna Specimen No?
table(table(THA_ASL$`Dna Specimen No`, useNA = "always"), useNA = "always")
```

Nope, no duplicates, great news.
```{r asl_duplicates_THA_troll}
THA_samples <- bind_rows(KTROL18THA.gcl$attributes, KGILL18THA.gcl$attributes, KSEIN18THA.gcl$attributes) %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  pull(`Dna Specimen No`)
```

Cool, none of our ASL duplicate Dna Specimen No are in there. Now verify that all winter samples are in the ASL data.
```{r THA_in_asl}
all(THA_samples %in% THA_ASL$`Dna Specimen No`)
```

Now that we've verified that all genotyped samples are in the ASL data, pool all sillys into one THA silly, then join with attributes to get quadrant level information.
```{r join_THA_asl}
# Pool
PoolCollections.GCL(collections = THA_2018_sillys, loci = GAPSLoci_reordered, newname = "KTHA18")

# Join ASL with attributes table
KTHA18.gcl$attributes <- KTHA18.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(THA_ASL, by = "Dna Specimen No")
```

How many fish per stat area by gear and stat week?
```{r THA_stat_area_counts}
KTHA18.gcl$attributes %>% 
  count(Gear, `Stat Week`, `Stat Area`) %>% 
  spread(`Stat Week`, n) %>% 
  arrange(`Stat Area`)
```

Create a variable for mixture for ease of pooling into separate mixtures.
```{r THA_attributes_mixture}
KTHA18.gcl$attributes <- KTHA18.gcl$attributes %>% 
  mutate(mixture = case_when(`Stat Area` == "101-95" & `Stat Week` %in% 18:23 ~ "neets_sw18_23",
                             `Stat Area` == "101-95" & `Stat Week` %in% 24 ~ "neets_sw24",
                             `Stat Area` == "101-95" & `Stat Week` %in% 25:27 ~ "neets_sw25_27",
                             `Stat Area` == "107-35" & `Stat Week` %in% 20:21 ~ "anita_sw20_21",
                             `Stat Area` == "107-35" & `Stat Week` %in% 22 ~ "anita_sw22",
                             `Stat Area` == "107-35" & `Stat Week` %in% 23 ~ "anita_sw23",
                             `Stat Area` == "107-35" & `Stat Week` %in% 24 ~ "anita_sw24",
                             `Stat Area` == "107-35" & `Stat Week` %in% 25:30 ~ "anita_sw25_30"))

KTHA18.gcl$attributes %>% 
  count(mixture)
```


# Define mixture strata

THA mixtures are each stat area and stat week. Each mixture has ~ 100 fish. We are doing 3 mixtures for Neets Bay (101-95) and 5 mixtures for Anita Bay (107-35).

  * THA
    + 10195 (Neets Bay)
        - SW 18-23
        - SW 24
        - SW 25-27
    + 10735 (Anita Bay)
        - SW 20-21
        - SW 22
        - SW 23
        - SW 24
        - SW 25-30

Create THA mixtures.
```{r THA_define_mixtures}
Neets_SW18_23.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "neets_sw18_23")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Neets_SW18_23.vials, newname = "Neets_SW18_23")

Neets_SW24.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "neets_sw24")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Neets_SW24.vials, newname = "Neets_SW24")

Neets_SW25_27.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "neets_sw25_27")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Neets_SW25_27.vials, newname = "Neets_SW25_27")

Anita_SW20_21.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "anita_sw20_21")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Anita_SW20_21.vials, newname = "Anita_SW20_21")

Anita_SW22.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "anita_sw22")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Anita_SW22.vials, newname = "Anita_SW22")

Anita_SW23.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "anita_sw23")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Anita_SW23.vials, newname = "Anita_SW23")

Anita_SW24.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "anita_sw24")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Anita_SW24.vials, newname = "Anita_SW24")

Anita_SW25_30.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTHA18", attribute = "mixture", matching = "anita_sw25_30")), nm = "KTHA18")
PoolCollections.GCL(collections = "KTHA18", loci = GAPSLoci_reordered, IDs = Anita_SW25_30.vials, newname = "Anita_SW25_30")

sapply(grep(pattern = "_SW", objects(pattern = "\\.gcl"), value = TRUE), function(silly) {get(silly)$n})
```

Save genotypes for THA strata.
```{r save_THA_strata_genotypes}
if(!dir.exists("../Genotypes/strata")) {dir.create("../Genotypes/strata")}

THA_2018_mixnames <- gsub(pattern = ".gcl", replacement = '', x = grep(pattern = "_SW", objects(pattern = "\\.gcl"), value = TRUE))

save_objects(objects = "THA_2018_mixnames", path = "../Objects/")
save_sillys(sillyvec = THA_2018_mixnames, path = "../Genotypes/strata/")
```

# Data QA

Standard data QA:

  * Remove fish missing <80% genotypes
  * Remove duplicates (>95% genotype concordance)

```{r THA_QA}
# original sample sizes
THA_2018_sample_sizes <- tibble(silly = THA_2018_mixnames,
                                genotyped = sapply(THA_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# missing
THA_2018_missing <- RemoveIndMissLoci.GCL(sillyvec = THA_2018_mixnames, proportion = 0.8)
save_objects("THA_2018_missing", "../Objects/")

THA_2018_sample_sizes <- THA_2018_sample_sizes %>% 
  mutate(missing = genotyped - sapply(THA_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# duplicate
THA_2018_duplicates <- CheckDupWithinSilly.GCL(sillyvec = THA_2018_mixnames, loci = GAPSLoci_reordered, quantile = NULL, minproportion = 0.95)
(THA_2018_duplicates_summary <- sapply(THA_2018_mixnames, function(x) {THA_2018_duplicates[[x]]$report}))
save_objects("THA_2018_duplicates_summary", "../Objects/")

THA_2018_duplciates_removed <- RemoveDups.GCL(dupcheck = THA_2018_duplicates)

THA_2018_sample_sizes <- THA_2018_sample_sizes %>% 
  mutate(duplicate = genotyped - missing - sapply(THA_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# final
THA_2018_sample_sizes <- THA_2018_sample_sizes %>% 
  mutate(final = sapply(THA_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))
THA_2018_sample_sizes
save_objects("THA_2018_sample_sizes", "../Objects/")

write_csv(THA_2018_sample_sizes, "../Tables/THA_2018_sample_sizes.csv")
```

Save post-QA genotypes
```{r THA_post_QA}
if(!dir.exists("../Genotypes/strata_postQA/")) {dir.create("../Genotypes/strata_postQA/")}
save_sillys(sillyvec = THA_2018_mixnames, path = "../Genotypes/strata_postQA")
```

# Create *BAYES* files

## Directory setup

First need to set up *BAYES* directory structure and copy over baseline file and *BAYES* objects. This was already done when we ran TBR.
```{r THA_BAYES_setup, results='hide'}
# dir.create(path = "../BAYES")
# sapply(c("Baseline", "Control", "Mixture", "Output"), function(folder) {dir.create(path = paste("../BAYES", folder, sep = "/"))} )
# 
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/SEAKPops357.txt", to = "../Objects")
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/bayesfortran_357.txt", to = "../Objects")
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/BAYES/Baseline/GAPS357pops13loci.bse", to = "../BAYES/Baseline")
# file.copy(from = "V:/Analysis/4_Westward/Sockeye/KMA Commercial Harvest 2014-2016/Mixtures/Objects/WASSIPSockeyeSeeds.txt", to = "../Objects")
# 
# TBR_mixnames <- setNames(c("D108Gill_2018", "D111Gill_2018", "D111Sport_2018"), TBR_sillys)
# save_objects("TBR_mixnames", "../Objects/")
# load_objects("../Objects/")
```

## Create mixtures

Save the fortran format and create TBR *BAYES* mixture files. This was already done when we ran TBR.
```{r THA_BAYES_mixtures}
# mixfortran <- CreateMixture.GCL(sillys = TBR_sillys[1], loci = GAPSLoci_reordered, IDs = NULL, mixname = TBR_mixnames[TBR_sillys[1]], dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
# save_objects("mixfortran", "../Objects/")

sapply(THA_2018_mixnames, function(mix) {
  CreateMixture.GCL(sillys = mix, loci = GAPSLoci_reordered, IDs = NULL, mixname = mix, dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
} )
```

## Create priors

New this year, I will be analyzing **ALL** Chinook mixtures with the full 33 reporting groups. Also a new wrinkle because we've never ran any THA mixtures, I'm not entirely sure what to use as a good prior. After talking with Sara, we agreed to do a rolling prior. For the first mixture for each area, we agreed to put 90% of the prior weight on the reporting group for the brood source released in each location (Neets-Chickamin and Anita-Andrew) and spread the rest out among all other reporting groups. Not ideal, but better than a group flat prior or anything else we could think of.

Now create 2018 priors.
```{r THA_create_2018_priors}
# Put prior weight on Andrew Creek for Anita (Andrew brood source)
Anita_SW20_21_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = as.numeric(GroupNames33 == "Andrew"), minval = 0.003125) # this puts 90% prior weight on Andrew

# Put prior weight on SSEAK for Neets (Chickamin brood source)
Neets_SW18_23_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = as.numeric(GroupNames33 == "SSEAK"), minval = 0.003125) # this puts 90% prior weight on SSEAK

save_objects(c("Anita_SW20_21_2018_prior", "Neets_SW18_23_2018_prior"), "../Objects/")
```

## Create control files

Now that we have priors, just need to create *BAYES* control files for the first Neets and Anita runs.
```{r THA_BAYES_control}
CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Anita_SW20_21", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Anita_SW20_21_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")

CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Neets_SW18_23", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Neets_SW18_23_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")
```

## Create output directories

```{r THA_BAYES_output}
sapply(THA_2018_mixnames, function(mix) {dir.create(paste0("../BAYES/Output/", mix))} )
```

## Summarize *BAYES* output for rolling prior

Need to quickly summarize the output from Anita_SW20_21 and Neets_SW18_23 for rolling prior.
```{r THA_rolling_prior_1}
Anita_SW20_21_estimates_33RG <- CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, 
                                                             maindir = "../BAYES/Output/", mixvec = THA_2018_mixnames[1],
                                                             prior = '', ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1,
                                                             PosteriorOutput = FALSE)

Anita_SW22_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = Anita_SW20_21_estimates_33RG[[1]][, "mean"], minval = 0.01)
save_objects(objects = "Anita_SW22_2018_prior", path = "../Objects/")

CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Anita_SW22", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Anita_SW22_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")


Neets_SW18_23_estimates_33RG <- CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, 
                                                             maindir = "../BAYES/Output/", mixvec = THA_2018_mixnames[6],
                                                             prior = '', ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1,
                                                             PosteriorOutput = FALSE)

Neets_SW24_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = Neets_SW18_23_estimates_33RG[[1]][, "mean"], minval = 0.01)
save_objects(objects = "Neets_SW24_2018_prior", path = "../Objects/")

CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Neets_SW24", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Neets_SW24_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")
```

Need to quickly summarize the output from Anita_SW22 and Neets_SW24 for rolling prior.
```{r THA_rolling_prior_2}
Anita_SW22_estimates_33RG <- CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, 
                                                          maindir = "../BAYES/Output/", mixvec = THA_2018_mixnames[2],
                                                          prior = '', ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1,
                                                          PosteriorOutput = FALSE)

Anita_SW23_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = Anita_SW22_estimates_33RG[[1]][, "mean"], minval = 0.01)
save_objects(objects = "Anita_SW23_2018_prior", path = "../Objects/")

CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Anita_SW23", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Anita_SW23_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")


Neets_SW24_estimates_33RG <- CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, 
                                                          maindir = "../BAYES/Output/", mixvec = THA_2018_mixnames[7],
                                                          prior = '', ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1,
                                                          PosteriorOutput = FALSE)

Neets_SW25_27_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = Neets_SW24_estimates_33RG[[1]][, "mean"], minval = 0.01)
save_objects(objects = "Neets_SW25_27_2018_prior", path = "../Objects/")

CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Neets_SW25_27", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Neets_SW25_27_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")
```

Need to quickly summarize the output from Anita_SW23 for rolling prior.
```{r THA_rolling_prior_3}
Anita_SW23_estimates_33RG <- CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, 
                                                          maindir = "../BAYES/Output/", mixvec = THA_2018_mixnames[3],
                                                          prior = '', ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1,
                                                          PosteriorOutput = FALSE)

Anita_SW24_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = Anita_SW23_estimates_33RG[[1]][, "mean"], minval = 0.01)
save_objects(objects = "Anita_SW24_2018_prior", path = "../Objects/")

CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Anita_SW24", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Anita_SW24_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")
```

Need to quickly summarize the output from Anita_SW24 for rolling prior.
```{r THA_rolling_prior_4}
Anita_SW24_estimates_33RG <- CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, 
                                                          maindir = "../BAYES/Output/", mixvec = THA_2018_mixnames[4],
                                                          prior = '', ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1,
                                                          PosteriorOutput = FALSE)

Anita_SW25_30_2018_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = Anita_SW24_estimates_33RG[[1]][, "mean"], minval = 0.01)
save_objects(objects = "Anita_SW25_30_2018_prior", path = "../Objects/")

CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = "Anita_SW25_30", basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                      nchains = 5, groupvec = GroupVec33RG_357, priorvec = Anita_SW25_30_2018_prior, initmat = GAPS357PopsInits, 
                      dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                      basefortran = bayesfortran_357, switches = "F T F T T T F")
```

# Summarize *BAYES* results

Summarize results for both the full 33 reporting groups and the custom 5 THA reporting groups.

## 33 reporting groups

Create standard summary and tall tibble, save both.
```{r BAYES_summarise_THA_33RG}
# full 33 reporting groups
THA_2018_33RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, maindir = "../BAYES/Output", mixvec = THA_2018_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
THA_2018_33RG_estimates.tdy <- 
  bind_rows(
    lapply(THA_2018_mixnames, function(mix) {  # loop over mixture names
      THA_2018_33RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("THA", "SW_range"), sep = "_SW", remove = FALSE) %>%  # extract mixture and year
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames33))  # factor for ordering

save_objects(c("THA_2018_33RG_EstimatesStats", "THA_2018_33RG_estimates.tdy"), "../Estimates objects")
```

## 5 THA reporting groups

Create standard summary and tall tibble, save both.
```{r BAYES_summarise_THA_5RG}
GroupNames5_THA <- c("Andrew", "TBR", "SSEAK", "Other SEAK", "Other")
GroupVec5RG_THA_33 <- c(4, 2, 4, 4, 2, 1, 2, 3, rep(5, 25))

THA_2018_5RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = GroupVec5RG_THA_33, groupnames = GroupNames5_THA, maindir = "../BAYES/Output", 
                               mixvec = THA_2018_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
THA_2018_5RG_estimates.tdy <- 
  bind_rows(
    lapply(THA_2018_mixnames, function(mix) {  # loop over mixture names
      THA_2018_5RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("THA", "SW_range"), sep = "_SW", remove = FALSE) %>%  # extract mixture and year
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames5_THA))  # factor for ordering

save_objects(c("GroupNames5_THA", "GroupVec5RG_THA_33"), "../Objects")
save_objects(c("THA_2018_5RG_EstimatesStats", "THA_2018_5RG_estimates.tdy"), "../Estimates objects")
```

# Plot THA 5RG

```{r THA_plots}
THA_2018_5RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(THA == "Anita") %>% 
  ggplot(aes(x = SW_range, y = mean, group = group, fill = group)) +
  geom_col(width = 0.7, position = position_dodge(0.8)) +
  geom_errorbar(aes(ymin = `5%`, ymax = `95%`), width = 0.4, position = position_dodge(0.8)) +
  ylim(c(0, 100)) +
  ylab("Stock Composition (%)") +
  xlab("Stat Week Range") +
  guides(fill = guide_legend(title = "Reporting Group")) +
  facet_grid(. ~ THA)

THA_2018_5RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(THA == "Neets") %>% 
  ggplot(aes(x = SW_range, y = mean, group = group, fill = group)) +
  geom_col(width = 0.7, position = position_dodge(0.8)) +
  geom_errorbar(aes(ymin = `5%`, ymax = `95%`), width = 0.4, position = position_dodge(0.8)) +
  ylim(c(0, 100)) +
  ylab("Stock Composition (%)") +
  xlab("Stat Week Range") +
  guides(fill = guide_legend(title = "Reporting Group")) +
  facet_grid(. ~ THA)
```


# Spring troll: import mixture genotypes

Read in genotypes from *LOKI* as `.gcl` objects. Save in directory.
```{r spring_loki}
# origins_sillys <- c("KTROL17EW", "KTROL18LW", "KTROL18SP", "KTROL18SU", "KSPORT18", "KTROL18THA", "KGILL18THA", "KSEIN18THA")
spring_2018_sillys <- c("KTROL18SP")
LOKI2R_GAPS.GCL(sillyvec = spring_2018_sillys, username = .username, password = .password)
rm(.username, .password)

sapply(spring_2018_sillys, function(silly) {get(paste0(silly, ".gcl"))$n} )

save_sillys(sillyvec = spring_2018_sillys, path = "../Genotypes/original")
save_objects(objects = c("spring_2018_sillys"), path = "../Objects/")
```

# Join ASL

## Spring Troll

Read in the troll ASL data.
```{r spring_asl, message=FALSE}
(spring_ASL <- read_csv(file = "../ASL Data/2018 Spring Troll Chinook ASLDist Subdistrict.csv") %>% 
   select(`Sample Date`, `Stat Week`, `Port Code`, `Gear`, `Quadrant`, `District`, `Sub/District`, `Dna Specimen No`, `Cwt Strap Tag No`))

# Any duplicate Dna Specimen No?
table(table(spring_ASL$`Dna Specimen No`, useNA = "always"), useNA = "always")
```

Shit, it looks like we have some duplicate Dna Specimen No (1 to be precise). Resolved.
```{r spring_asl_duplicates}
asl_duplicates <- spring_ASL %>% 
  group_by(`Dna Specimen No`) %>% 
  summarise(n = n()) %>% 
  filter(n > 1) %>% 
  pull(`Dna Specimen No`)

spring_ASL %>% 
  filter(`Dna Specimen No` %in% asl_duplicates) %>% 
  arrange(`Dna Specimen No`)
```

Are any of these fish in our spring troll samples?
```{r asl_duplicates_spring_troll}
spring_samples <- KTROL18SP.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  pull(`Dna Specimen No`)

any(spring_samples %in% asl_duplicates)
```

Yes, this sample is in there twice, they are clearly different fish. One has scale card number 4, the other has 8, I will change the fish with scale card 8 to 587408 in the .csv file.

Cool, none of our ASL duplicate Dna Specimen No are in there. Now verify that all spring samples are in the ASL data.
```{r spring_in_asl}
all(spring_samples %in% spring_ASL$`Dna Specimen No`)
```

Excellent, all samples accounted for!!!

Need to fix Month so it doesn't rely solely on Sample Date, (some fish sampled on June 1 were harvested in May).
```{r spring_asl_statarea}
spring_ASL <- spring_ASL %>% 
  mutate(Subdistrict = str_pad(string = `Sub/District`, width = 2, side = "left", pad = 0)) %>% 
  unite(`Stat Area`, c("District", "Subdistrict"), sep = "", remove = FALSE) %>% 
  mutate(`Sample Date` = mdy(`Sample Date`)) %>% 
  mutate(Month = month(`Sample Date`, label = TRUE, abbr = FALSE))
```

Now that we've resolved our ASL discrepancy, join with attributes to get stat area level information.
```{r join_spring_asl}
# Join ASL with attributes table
# Spring
KTROL18SP.gcl$attributes <- KTROL18SP.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(spring_ASL, by = "Dna Specimen No")
```

How many fish per stat area and month??
```{r spring_stat_area_counts}
KTROL18SP.gcl$attributes %>% 
  count(`Stat Area`, Month) %>% 
  spread(Month, n, fill = 0)
```

# Define mixture strata

Spring mixtures are each stat area and month by itself.

Create spring mixtures.
```{r spring_define_mixtures}
EWintNO_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 171)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintNO_2018.vials, newname = "EWintNO_2018")

EWintSO_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 172)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintSO_2018.vials, newname = "EWintSO_2018")

EWintNI_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 173)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintNI_2018.vials, newname = "EWintNI_2018")

EWintSI_2018.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KTROL17EW", attribute = "District", matching = 174)), nm = "KTROL17EW")
PoolCollections.GCL(collections = "KTROL17EW", loci = GAPSLoci_reordered, IDs = EWintSI_2018.vials, newname = "EWintSI_2018")

sapply(grep(pattern = "EWint", objects(pattern = "\\.gcl"), value = TRUE), function(silly) {get(silly)$n})
```

Save genotypes for spring strata.
```{r save_spring_strata_genotypes}
if(!dir.exists("../Genotypes/strata")) {dir.create("../Genotypes/strata")}

spring_2018_mixnames <- c(paste0("EWint", c("NO", "SO", "NI", "SI"), "_2018"), 
                          paste0("LWint", c("NO", "SO", "NI", "SI"), "_2018"))

save_objects(objects = "spring_2018_mixnames", path = "../Objects/")
save_sillys(sillyvec = spring_2018_mixnames, path = "../Genotypes/strata/")
```

# Data QA

Standard data QA:

  * Remove fish missing <80% genotypes
  * Remove duplicates (>95% genotype concordance)

```{r spring_QA}
# original sample sizes
spring_2018_sample_sizes <- tibble(silly = spring_2018_mixnames,
                                   genotyped = sapply(spring_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# missing
spring_2018_missing <- RemoveIndMissLoci.GCL(sillyvec = spring_2018_mixnames, proportion = 0.8)
save_objects("spring_2018_missing", "../Objects/")

spring_2018_sample_sizes <- spring_2018_sample_sizes %>% 
  mutate(missing = genotyped - sapply(spring_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# duplicate
spring_2018_duplicates <- CheckDupWithinSilly.GCL(sillyvec = spring_2018_mixnames, loci = GAPSLoci_reordered, quantile = NULL, minproportion = 0.95)
(spring_2018_duplicates_summary <- sapply(spring_2018_mixnames, function(x) {spring_2018_duplicates[[x]]$report}))
save_objects("spring_2018_duplicates_summary", "../Objects/")

spring_2018_duplciates_removed <- RemoveDups.GCL(dupcheck = spring_2018_duplicates)

spring_2018_sample_sizes <- spring_2018_sample_sizes %>% 
  mutate(duplicate = genotyped - missing - sapply(spring_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# final
spring_2018_sample_sizes <- spring_2018_sample_sizes %>% 
  mutate(final = sapply(spring_2018_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))
spring_2018_sample_sizes
save_objects("spring_2018_sample_sizes", "../Objects/")

write_csv(spring_2018_sample_sizes, "../Tables/spring_2018_sample_sizes.csv")
```

Save post-QA genotypes
```{r spring_post_QA}
if(!dir.exists("../Genotypes/strata_postQA/")) {dir.create("../Genotypes/strata_postQA/")}
save_sillys(sillyvec = spring_2018_mixnames, path = "../Genotypes/strata_postQA")
```

# Create *BAYES* files

## Directory setup

First need to set up *BAYES* directory structure and copy over baseline file and *BAYES* objects. This was already done when we ran TBR.
```{r spring_BAYES_setup, results='hide'}
# dir.create(path = "../BAYES")
# sapply(c("Baseline", "Control", "Mixture", "Output"), function(folder) {dir.create(path = paste("../BAYES", folder, sep = "/"))} )
# 
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/SEAKPops357.txt", to = "../Objects")
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/bayesfortran_357.txt", to = "../Objects")
# file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/BAYES/Baseline/GAPS357pops13loci.bse", to = "../BAYES/Baseline")
# file.copy(from = "V:/Analysis/4_Westward/Sockeye/KMA Commercial Harvest 2014-2016/Mixtures/Objects/WASSIPSockeyeSeeds.txt", to = "../Objects")
# 
# TBR_mixnames <- setNames(c("D108Gill_2018", "D111Gill_2018", "D111Sport_2018"), TBR_sillys)
# save_objects("TBR_mixnames", "../Objects/")
# load_objects("../Objects/")
```

## Create mixtures

Save the fortran format and create TBR *BAYES* mixture files. This was already done when we ran TBR.
```{r spring_BAYES_mixtures}
# mixfortran <- CreateMixture.GCL(sillys = TBR_sillys[1], loci = GAPSLoci_reordered, IDs = NULL, mixname = TBR_mixnames[TBR_sillys[1]], dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
# save_objects("mixfortran", "../Objects/")

sapply(spring_2018_mixnames, function(mix) {
  CreateMixture.GCL(sillys = mix, loci = GAPSLoci_reordered, IDs = NULL, mixname = mix, dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
} )
```

## Create priors

New this year, I will be analyzing **ALL** Chinook mixtures with the full 33 reporting groups. However, since I ran last year's troll mixtures for just the 26 reporting groups, I will have to mess with the priors a bit. Also a new wrinkle because we've previously ran NISISO together for Early and Late Winter. I think to keep things simple, I'll use the previous year's NISISO estimate for the prior for each of those respective quadrants (NI, SI, and SO)
```{r spring_read_2017_estimates}
Spring_2017_26RG_EstimatesStats <- dget("../../SEAK17/Estimates objects/Spring_2017_26RG_StratifiedEstimatesStats.txt")

(winter_2017_means <- sapply(c(EWint_2017_26RG_EstimatesStats, LWint_2017_26RG_EstimatesStats), function(mix) {mix[, "mean"]}))
```

My plan is to keep the same prior for the 26 groups and then spread out the prior evenly across all other 33 reporting groups.
```{r spring_setup_2018_priors}
# Convert from 26RG to 33RG
winter_2017_means_33RG <- apply(winter_2017_means, 2, function(mix) {mix[GroupVec33RG_to26RG] / table(GroupVec33RG_to26RG)[GroupVec33RG_to26RG]} )
rownames(winter_2017_means_33RG) <- GroupNames33

# Duplicate NISISO to NI, SI, SO
winter_2017_means_33RG <- winter_2017_means_33RG[, c(1, 2, 2, 2, 3, 4, 4, 4)]

# Fix dimnames
colnames(winter_2017_means_33RG) <- winter_2018_mixnames

# Verify
apply(winter_2017_means_33RG, 2, sum)
```

Now create 2018 priors.
```{r spring_create_2018_priors}
winter_2018_priors <- apply(winter_2017_means_33RG, 2, function(mix) {
  Prior.GCL(groupvec = GroupVec33RG_357, groupweights = mix, minval = 0.01)
} )
colnames(winter_2018_priors) <- winter_2018_mixnames
save_objects("winter_2018_priors", "../Objects/")
```

## Create control files

Now that we have priors, just need to create *BAYES* control files.
```{r spring_BAYES_control}
sapply(winter_2018_mixnames, function(mix) {
  CreateControlFile.GCL(sillyvec = SEAKPops357, loci = GAPSLoci_reordered, mixname = mix, basename = "GAPS357pops13loci", suffix = "", nreps = 40000,
                        nchains = 5, groupvec = GroupVec33RG_357, priorvec = winter_2018_priors[, mix], initmat = GAPS357PopsInits, 
                        dir = "../BAYES/Control", seeds = WASSIPSockeyeSeeds, thin = c(1, 1, 100), mixfortran = mixfortran, 
                        basefortran = bayesfortran_357, switches = "F T F T T T F")
} )

```

## Create output directories

```{r spring_BAYES_output}
sapply(winter_2018_mixnames, function(mix) {dir.create(paste0("../BAYES/Output/", mix))} )
```


