---
title: "Estimates Tables for Report"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup}
source("~/../R/Functions.GCL.R")
library(tidyverse)
library(lubridate)
library(xlsx)
load_objects("../Objects/")
```

# Purpose
The purpose of this short notebook is to generate publication ready tables for the 2018 Troll + Sport Chinook GSI report

# 8RG Summary Tables

## Estimates objects

Get objects
```{r}
(
  SEAK18estimatesobjects <-
    list.files(
      path = "../Estimates objects",
      recursive = FALSE,
      pattern = "_8RG"
    )
)
```

Load objects
```{r}
load_objects(path = "../Estimates objects", pattern = "Troll2018_8RG")
```

Verify
```{r}
names(Troll2018_8RG_EstimatesStats)
```

Add in the annual stratified estimates
```{r}
Troll2018_8RG_EstimatesStats <- c(Troll2018_8RG_EstimatesStats, list("Annual_2018" = AllYearTroll2018_8RG_StratifiedEstimatesStats))
```

## Check GR

```{r}
any(sapply(Troll2018_8RG_EstimatesStats, function(mix) {any(mix[, "GR"] > 1.2)}))
```

## Reformat estimates stats

```{r}
(
  Troll2018_8RG_EstimatesStats_Formatted <-
    sapply(Troll2018_8RG_EstimatesStats, function(yr) {
      matrix(
        data = yr[, 1:5],
        nrow = 8,
        ncol = 5,
        dimnames = list(GroupNames8Pub, c("Mean", "SD", "Median", "5%", "95%"))
      )
    }, simplify = FALSE)
)
```

Save
```{r}
save_objects(objects = "Troll2018_8RG_EstimatesStats_Formatted", path = "../Estimates objects/")
```

```{r}
names(Troll2018_8RG_EstimatesStats_Formatted)
```

Rename
```{r}
(Troll2018_8RG_PubNames <-
   setNames(
     object = c(
       "Early Winter Northern Outside Quadrant",
       "Early Winter All Quadrants",
       "Late Winter Northern Outside Quadrant",
       "Late Winter All Quadrants",
       "Spring Northern Outside Quadrant",
       "Spring Southern Inside Quadrant",
       "Spring All Quadrants",
       "Summer Retention 1 Northern Outside Quadrant",
       "Summer Retention 1 All Quadrants",
       "Summer Retention 2 Northern Outside Quadrant",
       "Summer Retention 2 All Quadrants",
       "AY 2018 Annual"
     ),
     nm = names(Troll2018_8RG_EstimatesStats_Formatted)
   ))

save_objects(objects = "Troll2018_8RG_PubNames", path = "../Objects")
```

## Sample Sizes

```{r}
objects(pattern = "sample")
```
Get sample sizes
```{r}
(
  sample_sizes_2018 <-
    dplyr::bind_rows(
      winter_2018_sample_sizes,
      spring_2018_sample_sizes,
      summer_2018_sample_sizes,
      sport_2018_sample_sizes
    )
)
```

Match sample sizes up to stratified estimates
```{r}
(Troll2018_8RG_MixNames <- setNames(
  object = list(
    "EWintNO_2018",
    winter_2018_mixnames[1:4],
    "LWintNO_2018",
    winter_2018_mixnames[5:8],
    spring_2018_mixnames[c(1, 8, 9, 5, 10, 2)],
    spring_2018_mixnames[c(3, 6)],
    spring_2018_mixnames[c(3, 6, 4, 7, 1, 8, 9, 5, 10, 2)],
    "SummerRet1NO_2018",
    summer_2018_mixnames[1:4],
    "SummerRet2NO_2018",
    summer_2018_mixnames[5:8],
    c(winter_2018_mixnames, spring_2018_mixnames, summer_2018_mixnames)
  ),
  nm = names(Troll2018_8RG_EstimatesStats_Formatted)
))

save_objects(objects = "Troll2018_8RG_MixNames", path = "../Objects")
```

Get sample sizes
```{r}
(Troll2018_8RG_SampleSizes <-
   sapply(Troll2018_8RG_MixNames, function(mix) {
     sample_sizes_2018 %>%
       filter(silly %in% mix) %>%
       summarise(n = sum(final)) %>% 
       pull(n)
   }))
```

## Create fully formatted spreadsheat

```{r}
EstimatesStats <- Troll2018_8RG_EstimatesStats_Formatted
SampSizes <- Troll2018_8RG_SampleSizes
PubNames <- Troll2018_8RG_PubNames
```

```{r}
for(mix in names(EstimatesStats)) {
  TableX <- matrix(data = "",
                   nrow = 11,
                   ncol = 7)
  TableX[1, 3] <- paste(PubNames[mix], " (n=", SampSizes[mix], ")")
  TableX[2, 6] <- "90% CI"
  TableX[3, 2:7] <-
    c("Reporting Group", colnames(EstimatesStats[[mix]]))
  TableX[4:11, 1] <- 1:8
  TableX[4:11, 2] <- rownames(EstimatesStats[[mix]])
  TableX[4:11, 3:7] <-
    formatC(x = EstimatesStats[[mix]],
            digits = 3,
            format = "f")
  
  xlsx::write.xlsx(
    x = TableX,
    file = "../Estimates tables/Troll2018_8RG_StratifiedEstimatesStats_FormattedPretty.xlsx",
    col.names = FALSE,
    row.names = FALSE,
    sheetName = paste(mix, " Troll 8 Driver"),
    append = TRUE
  )
  
}
```

# 4RG Summary Tables

## Estimates objects

Get objects
```{r}
(
  SEAK18estimatesobjects <-
    list.files(
      path = "../Estimates objects",
      recursive = FALSE,
      pattern = "_4RG"
    )
)
```

Load objects
```{r}
load_objects(path = "../Estimates objects", pattern = "Troll2018_4RG_EstimatesStats")
load_objects(path = "../Estimates objects", pattern = "AllYearTroll2018_4RG")
```

Create nice summary object
```{r}
Troll2018_4RG_EstimatesStats <- list(
  "EWintNO_2018" = Troll_2018_Mixtures_4RG_EstimatesStats[["EWintNO_2018"]],
  "EWintAllQuad_2018" = EWint_2018_4RG_StratifiedEstimatesStats,
  "LWintNO_2018" = Troll_2018_Mixtures_4RG_EstimatesStats[["LWintNO_2018"]],
  "LWintAllQuad_2018" = LWint_2018_4RG_StratifiedEstimatesStats,
  "SpringNO_2018" = SpringNO_2018_4RG_StratifiedEstimatesStats,
  "SpringSI_2018" = SpringSI_2018_4RG_StratifiedEstimatesStats,
  "SpringAllQuad_2018" = Spring_2018_4RG_StratifiedEstimatesStats,
  "SumRet1NO_2018" = Troll_2018_Mixtures_4RG_EstimatesStats[["SummerRet1NO_2018"]],
  "SumRet1AllQuad_2018" = SummerRet1_2018_4RG_StratifiedEstimatesStats,
  "SumRet2NO_2018" = Troll_2018_Mixtures_4RG_EstimatesStats[["SummerRet2NO_2018"]],
  "SumRet2AllQuad_2018" = SummerRet2_2018_4RG_StratifiedEstimatesStats
  )
save_objects(objects = "Troll2018_4RG_EstimatesStats", path = "../Estimates objects")
```

Verify
```{r}
names(Troll2018_4RG_EstimatesStats)
```

Add in the annual stratified estimates
```{r}
Troll2018_4RG_EstimatesStats <- c(Troll2018_4RG_EstimatesStats, list("Annual_2018" = AllYearTroll2018_4RG_StratifiedEstimatesStats))
```

## Check GR

```{r}
any(sapply(Troll2018_4RG_EstimatesStats, function(mix) {any(mix[, "GR"] > 1.2)}))
```

## Reformat estimates stats

```{r}
(
  Troll2018_4RG_EstimatesStats_Formatted <-
    sapply(Troll2018_4RG_EstimatesStats, function(yr) {
      matrix(
        data = yr[, 1:5],
        nrow = 4,
        ncol = 5,
        dimnames = list(GroupNames4Pub, c("Mean", "SD", "Median", "5%", "95%"))
      )
    }, simplify = FALSE)
)
```

Save
```{r}
save_objects(objects = "Troll2018_4RG_EstimatesStats_Formatted", path = "../Estimates objects/")
```

```{r}
names(Troll2018_4RG_EstimatesStats_Formatted)
```

Rename
```{r}
(Troll2018_4RG_PubNames <-
   setNames(
     object = c(
       "Early Winter Northern Outside Quadrant",
       "Early Winter All Quadrants",
       "Late Winter Northern Outside Quadrant",
       "Late Winter All Quadrants",
       "Spring Northern Outside Quadrant",
       "Spring Southern Inside Quadrant",
       "Spring All Quadrants",
       "Summer Retention 1 Northern Outside Quadrant",
       "Summer Retention 1 All Quadrants",
       "Summer Retention 2 Northern Outside Quadrant",
       "Summer Retention 2 All Quadrants",
       "AY 2018 Annual"
     ),
     nm = names(Troll2018_4RG_EstimatesStats_Formatted)
   ))

save_objects(objects = "Troll2018_4RG_PubNames", path = "../Objects")
```

## Sample Sizes

```{r}
objects(pattern = "sample")
```
Get sample sizes
```{r}
(
  sample_sizes_2018 <-
    dplyr::bind_rows(
      winter_2018_sample_sizes,
      spring_2018_sample_sizes,
      summer_2018_sample_sizes,
      sport_2018_sample_sizes
    )
)
```

Match sample sizes up to stratified estimates
```{r}
(Troll2018_4RG_MixNames <- setNames(
  object = list(
    "EWintNO_2018",
    winter_2018_mixnames[1:4],
    "LWintNO_2018",
    winter_2018_mixnames[5:8],
    spring_2018_mixnames[c(1, 8, 9, 5, 10, 2)],
    spring_2018_mixnames[c(3, 6)],
    spring_2018_mixnames[c(3, 6, 4, 7, 1, 8, 9, 5, 10, 2)],
    "SummerRet1NO_2018",
    summer_2018_mixnames[1:4],
    "SummerRet2NO_2018",
    summer_2018_mixnames[5:8],
    c(winter_2018_mixnames, spring_2018_mixnames, summer_2018_mixnames)
  ),
  nm = names(Troll2018_4RG_EstimatesStats_Formatted)
))

save_objects(objects = "Troll2018_4RG_MixNames", path = "../Objects")
```

Get sample sizes
```{r}
(Troll2018_4RG_SampleSizes <-
   sapply(Troll2018_4RG_MixNames, function(mix) {
     sample_sizes_2018 %>%
       filter(silly %in% mix) %>%
       summarise(n = sum(final)) %>% 
       pull(n)
   }))

save_objects(objects = "Troll2018_4RG_SampleSizes", "../Objects/")
```

## Create fully formatted spreadsheat

```{r}
EstimatesStats <- Troll2018_4RG_EstimatesStats_Formatted
SampSizes <- Troll2018_4RG_SampleSizes
PubNames <- Troll2018_4RG_PubNames
n_RG <- 4
```

```{r}
max_nrow = 3 + n_RG

for(mix in names(EstimatesStats)) {
  TableX <- matrix(data = "",
                   nrow = max_nrow,
                   ncol = 7)
  TableX[1, 3] <- paste(PubNames[mix], " (n=", SampSizes[mix], ")")
  TableX[2, 6] <- "90% CI"
  TableX[3, 2:7] <-
    c("Reporting Group", colnames(EstimatesStats[[mix]]))
  TableX[4:max_nrow, 1] <- 1:n_RG
  TableX[4:max_nrow, 2] <- rownames(EstimatesStats[[mix]])
  TableX[4:max_nrow, 3:7] <-
    formatC(x = EstimatesStats[[mix]],
            digits = 3,
            format = "f")
  
  xlsx::write.xlsx(
    x = TableX,
    file = "../Estimates tables/Troll2018_4RG_StratifiedEstimatesStats_FormattedPretty.xlsx",
    col.names = FALSE,
    row.names = FALSE,
    sheetName = paste(mix, " Troll 4RG"),
    append = TRUE
  )
  
}
```

# 18RG Summary Tables

## Estimates objects

Get objects
```{r}
(
  SEAK18estimatesobjects <-
    list.files(
      path = "../Estimates objects",
      recursive = FALSE,
      pattern = "_18RG"
    )
)
```

Load objects
```{r}
load_objects(path = "../Estimates objects", pattern = "18RG")
# load_objects(path = "../Estimates objects", pattern = "Troll2018_18RG_EstimatesStats")
# load_objects(path = "../Estimates objects", pattern = "AllYearTroll2018_18RG")
```

Create nice summary object
```{r}
Troll2018_18RG_EstimatesStats <- list(
  "EWintNO_2018" = Troll_2018_Mixtures_18RG_EstimatesStats[["EWintNO_2018"]],
  "EWintAllQuad_2018" = EWint_2018_18RG_StratifiedEstimatesStats,
  "LWintNO_2018" = Troll_2018_Mixtures_18RG_EstimatesStats[["LWintNO_2018"]],
  "LWintAllQuad_2018" = LWint_2018_18RG_StratifiedEstimatesStats,
  "SpringNO_2018" = SpringNO_2018_18RG_StratifiedEstimatesStats,
  "SpringSI_2018" = SpringSI_2018_18RG_StratifiedEstimatesStats,
  "SpringAllQuad_2018" = Spring_2018_18RG_StratifiedEstimatesStats,
  "SumRet1NO_2018" = Troll_2018_Mixtures_18RG_EstimatesStats[["SummerRet1NO_2018"]],
  "SumRet1AllQuad_2018" = SummerRet1_2018_18RG_StratifiedEstimatesStats,
  "SumRet2NO_2018" = Troll_2018_Mixtures_18RG_EstimatesStats[["SummerRet2NO_2018"]],
  "SumRet2AllQuad_2018" = SummerRet2_2018_18RG_StratifiedEstimatesStats
  )
save_objects(objects = "Troll2018_18RG_EstimatesStats", path = "../Estimates objects")
```

Verify
```{r}
names(Troll2018_18RG_EstimatesStats)
```

Add in the annual stratified estimates
```{r}
Troll2018_18RG_EstimatesStats <- c(Troll2018_18RG_EstimatesStats, list("Annual_2018" = AllYearTroll2018_18RG_StratifiedEstimatesStats))
```

## Check GR

```{r}
any(sapply(Troll2018_18RG_EstimatesStats, function(mix) {any(mix[, "GR"] > 1.2)}))
```

## Reformat estimates stats

```{r}
(
  Troll2018_18RG_EstimatesStats_Formatted <-
    sapply(Troll2018_18RG_EstimatesStats, function(yr) {
      matrix(
        data = yr[, 1:5],
        nrow = 18,
        ncol = 5,
        dimnames = list(GroupNames18Pub, c("Mean", "SD", "Median", "5%", "95%"))
      )
    }, simplify = FALSE)
)
```

Save
```{r}
save_objects(objects = "Troll2018_18RG_EstimatesStats_Formatted", path = "../Estimates objects/")
```

```{r}
names(Troll2018_18RG_EstimatesStats_Formatted)
```

## Create fully formatted spreadsheat

```{r}
EstimatesStats <- Troll2018_18RG_EstimatesStats_Formatted
SampSizes <- Troll2018_4RG_SampleSizes
PubNames <- Troll2018_4RG_PubNames
n_RG <- 18
```

```{r}
max_nrow = 3 + n_RG

for(mix in names(EstimatesStats)) {
  TableX <- matrix(data = "",
                   nrow = max_nrow,
                   ncol = 7)
  TableX[1, 3] <- paste(PubNames[mix], " (n=", SampSizes[mix], ")")
  TableX[2, 6] <- "90% CI"
  TableX[3, 2:7] <-
    c("Reporting Group", colnames(EstimatesStats[[mix]]))
  TableX[4:max_nrow, 1] <- 1:n_RG
  TableX[4:max_nrow, 2] <- rownames(EstimatesStats[[mix]])
  TableX[4:max_nrow, 3:7] <-
    formatC(x = EstimatesStats[[mix]],
            digits = 3,
            format = "f")
  
  xlsx::write.xlsx(
    x = TableX,
    file = "../Estimates tables/Troll2018_18RG_StratifiedEstimatesStats_FormattedPretty.xlsx",
    col.names = FALSE,
    row.names = FALSE,
    sheetName = paste(mix, " Troll 18RG"),
    append = TRUE
  )
  
}
```

# 33RG Summary Tables

## Estimates objects

Get objects
```{r}
(
  SEAK18estimatesobjects <-
    list.files(
      path = "../Estimates objects",
      recursive = FALSE,
      pattern = "_33RG"
    )
)
```

Load objects
```{r}
# load_objects(path = "../Estimates objects", pattern = "33RG")
load_objects(path = "../Estimates objects", pattern = "Troll_2018_Mixtures_33RG_EstimatesStats")
load_objects(path = "../Estimates objects", pattern = "2018_33RG_StratifiedEstimatesStats")
load_objects(path = "../Estimates objects", pattern = "AllYearTroll2018_33RG")
```

Create nice summary object
```{r}
Troll2018_33RG_EstimatesStats <- list(
  "EWintNO_2018" = Troll_2018_Mixtures_33RG_EstimatesStats[["EWintNO_2018"]],
  "EWintAllQuad_2018" = EWint_2018_33RG_StratifiedEstimatesStats,
  "LWintNO_2018" = Troll_2018_Mixtures_33RG_EstimatesStats[["LWintNO_2018"]],
  "LWintAllQuad_2018" = LWint_2018_33RG_StratifiedEstimatesStats,
  "SpringNO_2018" = SpringNO_2018_33RG_StratifiedEstimatesStats,
  "SpringSI_2018" = SpringSI_2018_33RG_StratifiedEstimatesStats,
  "SpringAllQuad_2018" = Spring_2018_33RG_StratifiedEstimatesStats,
  "SumRet1NO_2018" = Troll_2018_Mixtures_33RG_EstimatesStats[["SummerRet1NO_2018"]],
  "SumRet1AllQuad_2018" = SummerRet1_2018_33RG_StratifiedEstimatesStats,
  "SumRet2NO_2018" = Troll_2018_Mixtures_33RG_EstimatesStats[["SummerRet2NO_2018"]],
  "SumRet2AllQuad_2018" = SummerRet2_2018_33RG_StratifiedEstimatesStats
  )
save_objects(objects = "Troll2018_33RG_EstimatesStats", path = "../Estimates objects")
```

Verify
```{r}
names(Troll2018_33RG_EstimatesStats)
```

Add in the annual stratified estimates
```{r}
Troll2018_33RG_EstimatesStats <- c(Troll2018_33RG_EstimatesStats, list("Annual_2018" = AllYearTroll2018_33RG_StratifiedEstimatesStats))
```

## Check GR

```{r}
any(sapply(Troll2018_33RG_EstimatesStats, function(mix) {any(mix[, "GR"] > 1.2)}))
```

Which mixtures?
```{r}
which(sapply(Troll2018_33RG_EstimatesStats, function(mix) {any(mix[, "GR"] > 1.2)}))
```

Which RGs, how much contribution?
```{r}
sapply(Troll2018_33RG_EstimatesStats[c(8:9, 11:12)], function(x)
  x %>% as_tibble(rownames = "group"), simplify = FALSE) %>%
  bind_rows(.id = "mixture") %>%
  filter(GR > 1.2)
```

Low contributions, NBD.

## Reformat estimates stats

```{r}
GroupNames26Pub
GroupNames33
```

```{r}
GroupNames33Pub <- c(GroupNames26Pub[1:3],
                     "King Salmon",
                     GroupNames26Pub[4:8],
                     GroupNames26Pub[10:9],
                     "Lower Straight of Georgia",
                     GroupNames26Pub[11:12],
                     "Upper Straight of Georgia",
                     "Fraser Late",
                     "Fraser Early",
                     GroupNames26Pub[14:16],
                     "Straight of Juan de Fuca",
                     GroupNames26Pub[17:18],
                     "HoKo F",
                     GroupNames26Pub[c(19, 21, 20, 22)],
                     "Upper Columbia F",
                     "Upper Columbia Su",
                     GroupNames26Pub[24:26])

cbind(GroupNames33Pub, GroupNames33)
```

```{r}
save_objects(objects = "GroupNames33Pub", path = "../Objects")
```


```{r}
(
  Troll2018_33RG_EstimatesStats_Formatted <-
    sapply(Troll2018_33RG_EstimatesStats, function(yr) {
      matrix(
        data = yr[, 1:5],
        nrow = 33,
        ncol = 5,
        dimnames = list(GroupNames33Pub, c("Mean", "SD", "Median", "5%", "95%"))
      )
    }, simplify = FALSE)
)
```

Save
```{r}
save_objects(objects = "Troll2018_33RG_EstimatesStats_Formatted", path = "../Estimates objects/")
```

```{r}
names(Troll2018_33RG_EstimatesStats_Formatted)
```

## Create fully formatted spreadsheat

```{r}
EstimatesStats <- Troll2018_33RG_EstimatesStats_Formatted
SampSizes <- Troll2018_4RG_SampleSizes
PubNames <- Troll2018_4RG_PubNames
n_RG <- 33
```

```{r}
max_nrow = 3 + n_RG

for(mix in names(EstimatesStats)) {
  TableX <- matrix(data = "",
                   nrow = max_nrow,
                   ncol = 7)
  TableX[1, 3] <- paste(PubNames[mix], " (n=", SampSizes[mix], ")")
  TableX[2, 6] <- "90% CI"
  TableX[3, 2:7] <-
    c("Reporting Group", colnames(EstimatesStats[[mix]]))
  TableX[4:max_nrow, 1] <- 1:n_RG
  TableX[4:max_nrow, 2] <- rownames(EstimatesStats[[mix]])
  TableX[4:max_nrow, 3:7] <-
    formatC(x = EstimatesStats[[mix]],
            digits = 3,
            format = "f")
  
  xlsx::write.xlsx(
    x = TableX,
    file = "../Estimates tables/Troll2018_33RG_StratifiedEstimatesStats_FormattedPretty.xlsx",
    col.names = FALSE,
    row.names = FALSE,
    sheetName = paste(mix, " Troll 33RG"),
    append = TRUE
  )
  
}
```

















