---
title: "Winter + Spring Troll GSI Plots AY 2018"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, message=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE)
source("~/../R/Functions.GCL.R")
library(tidyverse)
library(lubridate)
load_objects("../Objects/")
load_objects("../Estimates objects/")
```

# Winter Troll

## Harvest

```{r winter_harvest, message=FALSE}
(winter_harvest <- read_csv("../Harvest Data/ft - Detailed Fish Tickets_traditional.csv") %>% 
  mutate(Month = month(`Date Fishing Ended`, label = TRUE, abbr = FALSE)) %>% 
  mutate(Fishery = case_when(Month %in% month.name[1:4] ~ "Late Winter",
                             Month %in% month.name[5] ~ "Spring Ret 1", 
                             Month %in% month.name[6] ~ "Spring Ret 2", 
                             Month %in% month.name[7] ~ "Summer Ret 1",
                             Month %in% month.name[8:9] ~ "Summer Ret 2",
                             Month %in% month.name[10:12] ~ "Early Winter"
                             )) %>% 
 mutate(Quadrant = case_when(District %in% c(113, 114, 116, 154, 156, 157, 181, 183, 189) ~ 171,
                             District %in% c(103, 104, 152) ~ 172,
                             District %in% c(109, 110, 111, 112, 115) ~ 173,
                             District %in% c(101, 102, 105, 106, 107, 108) ~ 174)) %>% 
  filter(Year == 2017 & Fishery == "Early Winter" | Year == 2018 & Fishery == "Late Winter") %>% 
  group_by(Quadrant, Fishery) %>% 
  summarise(Harvest = sum(`Number Of Animals (sum)`, na.rm = TRUE)) %>% 
  spread(Fishery, Harvest, fill = 0))
```

## Sample sizes

Final samples sizes for all Quadrant x Period. The original plan was to run ~200 fish for Late Winter NO, NI, and SI, however, I had to subsampled down in order to get the samples analyzed proportional to harvest by stat week.
```{r winter_n}
winter_2018_sample_sizes %>% 
  separate(silly, into = c("Fishery", "Year"), sep = "_") %>% 
  select(Fishery, genotyped, missing, duplicate, final)
```

## Stock composition
For each Quadrant and Period there will be a table showing stock composition results for all major stocks (i.e. those contributing > 5% to harvest).  
**Note** Late Winter NO, NI, and SI did not have as many samples run as planned (see above), thus we will need to discuss how many reporting groups we ultimately include. Take the results presented here with a grain of salt.

### Early Winter - Northern Outside (171)
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r winter_stock_comp_table_EWintNO}
winter_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "EWint" & quadrant == "NO") %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

```{r winter_troll_figures_EWintNO, out.width="100%"}
winter_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "EWint" & quadrant == "NO") %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Early Winter Troll AY 2018: Northern Outside 171")
```

### Early Winter - All Quadrants
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r winter_stock_comp_table_EWintAllQuad}
winter_2018_33RG_stratified_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "EWint") %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

```{r winter_troll_figures_EWintAllQuad, out.width="100%"}
winter_2018_33RG_stratified_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "EWint") %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Early Winter Troll AY 2018: All Quad")
```

### Late Winter - Northern Outside (171), Northern Inside (173), and Southern Inside (174)
What are the major stocks contributing to these mixtures (mean > 5%)?  
**Note** the sample sizes for these mixtures are <200 fish, so normally we would not report to this level of detail.
```{r winter_stock_comp_table_LWintNONISI}
winter_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "LWint" & quadrant != "SO") %>% 
  mutate(quadrant = factor(x = quadrant, levels = c("NO", "SO", "NI", "SI"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

```{r winter_troll_figures_LWintNONISI, out.width="100%", out.height="200%"}
winter_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "LWint" & quadrant != "SO") %>% 
  mutate(quadrant = factor(x = quadrant, levels = c("NO", "SO", "NI", "SI"))) %>%   ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Late Winter Troll AY 2018: Quadrant") +
  facet_grid(quadrant ~ .)
```

### Late Winter - All Quadrants
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r winter_stock_comp_table_LWintAllQuad}
winter_2018_33RG_stratified_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "LWint") %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

```{r winter_troll_figures_LWintAllQuad, out.width="100%"}
winter_2018_33RG_stratified_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "LWint") %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Late Winter Troll AY 2018: All Quad")
```


# Spring Troll

## Harvest

```{r spring_harvest, message=FALSE}
(spring_harvest <- read_csv("../Harvest Data/ft - Detailed Fish Tickets_spring.csv") %>% 
  mutate(Month = month(`Date Fishing Ended`, label = TRUE, abbr = FALSE)) %>% 
  group_by(`Stat Area`, Month) %>% 
  summarise(Harvest = sum(`Number Of Animals (sum)`, na.rm = TRUE)) %>% 
  spread(Month, Harvest, fill = 0))
```

## Sample sizes

Final samples sizes for all Stat Area x Month mixtures were ~200 fish (post-QA). 113-30 and 183-10 were run for the whole season with only ~100 samples each due to smaller harvests.
```{r spring_n}
spring_2018_sample_sizes %>% 
  separate(silly, into = c("period", "Stat Area", "Year"), sep = "_") %>% 
  mutate(Month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>%
  select(`Stat Area`, Month, genotyped, missing, duplicate, final)
```

## Stock composition
For each Stat Area there will be a table showing stock composition results for all major stocks (i.e. those contributing > 5% to harvest).  
**Note** Month = Spring means May + June. Final reporting for 183-10 and 113-30 will be for a smaller subset of reporting groups due to the limited sample size (~100 fish vs. ~200 fish in other mixtures), so those stock comps should be taken with a grain of salt.

### Mountain Point 101-45
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r spring_stock_comp_table_10145}
spring_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & stat_area == "10145") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(stat_area, month, desc(mean)) %>% 
  select(stat_area, month, group, mean, sd, `5%`, `95%`)
```

```{r spring_troll_figures_10145, out.width="100%"}
spring_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(stat_area == "10145") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Spring Troll AY 2018: Mountain Point 101-45") +
  facet_grid(month ~ .)
```

### Bucareli Bay 103-50
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r spring_stock_comp_table_10350}
spring_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & stat_area == "10350") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(stat_area, month, desc(mean)) %>% 
  select(stat_area, month, group, mean, sd, `5%`, `95%`)
```

```{r spring_troll_figures_10350, out.width="100%"}
spring_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(stat_area == "10350") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Spring Troll AY 2018: Bucareli Bay 103-50") +
  facet_grid(month ~ .)
```

### Western Chanel 113-01
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r spring_stock_comp_table_11301}
spring_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & stat_area == "11301") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(stat_area, month, desc(mean)) %>% 
  select(stat_area, month, group, mean, sd, `5%`, `95%`)
```

```{r spring_troll_figures_11301, out.width="50%"}
spring_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(stat_area == "11301") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Spring Troll AY 2018: Western Chanel 113-01") +
  facet_grid(month ~ .)
```

### Redoubt Bay 113-30
**Note** sample size is ~100 fish, take these with a grain of salt.
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r spring_stock_comp_table_11330}
spring_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & stat_area == "11330") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(stat_area, month, desc(mean)) %>% 
  select(stat_area, month, group, mean, sd, `5%`, `95%`)
```

```{r spring_troll_figures_11330, out.width="50%"}
spring_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(stat_area == "11330") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Spring Troll AY 2018: Redoubt Bay 113-30") +
  facet_grid(month ~ .)
```

### Sitka Sound 113-41
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r spring_stock_comp_table_11341}
spring_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & stat_area == "11341") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(stat_area, month, desc(mean)) %>% 
  select(stat_area, month, group, mean, sd, `5%`, `95%`)
```

```{r spring_troll_figures_11341, out.width="100%"}
spring_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(stat_area == "11341") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Spring Troll AY 2018: Sitka Sound 113-41") +
  facet_grid(month ~ .)
```

### Salisbury Sound 113-62
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r spring_stock_comp_table_11362}
spring_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & stat_area == "11362") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(stat_area, month, desc(mean)) %>% 
  select(stat_area, month, group, mean, sd, `5%`, `95%`)
```

```{r spring_troll_figures_11362, out.width="50%"}
spring_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(stat_area == "11362") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Spring Troll AY 2018: Salisbury Sound 113-62") +
  facet_grid(month ~ .)
```

### Yakutat Bay 183-10
**Note** sample size is ~100 fish, take these with a grain of salt.
What are the major stocks contributing to these mixtures (mean > 5%)?
```{r spring_stock_comp_table_18310}
spring_2018_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & stat_area == "18310") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(stat_area, month, desc(mean)) %>% 
  select(stat_area, month, group, mean, sd, `5%`, `95%`)
```

```{r spring_troll_figures_18310, out.width="50%"}
spring_2018_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(stat_area == "18310") %>% 
  mutate(month = case_when(period == "SpringRet1" ~ "May",
                           period == "SpringRet2" ~ "June", 
                           period == "Spring" ~ "Spring")) %>% 
  mutate(month = factor(x = month, levels = c("Spring", "May", "June"))) %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Spring Troll AY 2018: Yakutat Bay 183-10") +
  facet_grid(month ~ .)
```